Compositional equivalences based on Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-05-13 2016-Weak-FH-Bisim/WeakBisim.tex
notations

$
%\mprset {vskip=.5ex}
%\inferrule 
\Big(\forall i \in [1..n+1].\openrule
    {
       \set{\beta_{1i}},\Pred_{1i},\Post_{1i}   }
         {s_{1i} \OTarrow {\tau} s_{1(i+1)}} \in \mathcal{T} \,\wedge\,
\openrule
         {
           \set{\beta_2},\Pred_2,\Post_2 }
         {s_2 \OTarrow {\alpha} s'_2} \in \mathcal{T}
\, \wedge\\
~~\hspace{2.25cm}\forall i \in [0..m].\openrule
         {
           \set{\beta_{3i}},\Pred_{3i},\Post_{3i}   }
         {s_{3i} \OTarrow {\tau} s_{3(i+1)}}\! \in\! \mathcal{T}
\Big)  \implies\!  {
\openrule
         {
           \set{\gamma},
		\Pred, \Post
				 } {s'' \OTWeakarrow {\alpha'} s'} \in\WT
}
$
where\\
$
\alpha'=\alpha\displaystyle{\subst{\bigotimes_{j=n+1}^{1}\Post_j^1}}\\
s''=s_{10} \wedge s_{1(n+2)}=s_2 \wedge s'_2 = s_{30} \wedge s_{3(m+1)}=s'\\
\displaystyle{
\set{\gamma}=\mybigdotcup_{i=1}^{n+1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{1} \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=n+1}^{1}\Post_{1j}}} \dotcup \mybigdotcup_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}} }}
\\
\Pred=\bigwedge_{i=1}^{n+1}\Pred_{1i}\subst{\bigotimes_{j=i-1}^{1}\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j={n+1}}^{1}\Post_{1j}}\land\\ 
~\qquad\quad\Big(\bigwedge_{i=0}^m\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j={n+1}}^{1}\Post_{1j}}\Big)\\
\Post=\bigotimes_{j=m}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j={n+1}}^{1}\Post_{1j}
$

@@

\openrule
         {
           \beta_{2j}^{j\in J_2'},\Pred_2,\Post_2 }
         {s_{20} \OTarrow {\alpha} s_{21}} \in \mathcal{T}_1
 \wedge
\forall i \in [0..m].\openrule
         {
           \beta_{3ij}^{j\in J_3'},\Pred_{3i},  \Post_{3i}  }
         {s_{3i} \OTarrow {\tau} s_{3(i+1)}} \in \mathcal{T}_1
\bigg)
\end{mathpar}
where\\
$
s=s_{10} \wedge s_{1(n+1)}=s_{20} \wedge s_{21} = s_{30} \wedge s_{3(m+1)}=s'\\
\displaystyle{
\gamma_j^{j\in J'}=\mybigdotcup_{i=0}^n \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=n}^{0}\Post_{1j}}} \dotcup \mybigdotcup_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}} }}
\\
\Pred_{OT}=\bigwedge_{i=0}^n\Pred_{1i}\subst{\bigotimes_{j=i-1}^{0}\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j=n}^{0}\Post_{1j}}\land\\ 
~\qquad\quad\Big(\bigwedge_{i=0}^m\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}}\Big)\\
\Post_{OT}=\bigotimes_{j=m}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}$

For the sake of simplicity, we prove the rule in the  restricted case where $n$ and $m$ to be equal to $1$, hence a single tau open transition will be considered on each side of the potentially visible one. The proof may be easily generalized to the multiple tau open transitions by using the same reasoning and (\WTTrois)~rule. Consider each open transition separately:
\begin{enumerate}
\item For the first open transition in $\mathcal{T}_1$:
\begin{mathpar}
%\inferrule{
 \openrule
    {
       \beta_{1j}^{j\in J_1'},\Pred_1,\Post_1   }
         {s_{10} \OTarrow {\tau} s_{11}}          
\end{mathpar}
we have $(s,t|\Pred_{s,t})\in\mathcal{R}$ by hypothesis, and $s=s_{10}$ the we have $(s_{10},t|\Pred_{s_{10},t})\in\mathcal{R}$. Thus, by  Definition \ref{def-Weak-bisim} we  can deduce there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTWeakarrow {\alpha_x} t_x}
\end{mathpar}
 such that  $\forall x,J_{x}=\{j\in J_1'|\beta_{1j}\neq\tau\}, (s_{11},t_x|\Pred_{s_{11},t_x})\in \mathcal{R}$. \\
 $\Pred_{s,t} \land \Pred_1\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}}
  \!\! \left( \forall j\in J_x.\vis{\beta_{1j}}=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
     \land \alpha_x\!=\!\tau \land  
     \Pred_{s_{11},t_x}\subst{\Post_1\uplus\Post_{OT_x}}\right)$

Note that, because $\AlgE\cap\AlgA=\emptyset$  (actions and expressions are disjoint) and $\alpha_x\!=\!\tau$ we have 
directly ($\alpha_x$ cannot be a variable, and cannot contain expressions/variables because $\tau$ has no parameter):
\begin{mathpar}
    \openrule
         {
           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTWeakarrow {\tau} t_x}
\end{mathpar}
\item Concerning the middle open transition in $\mathcal{T}_1$, we have:
 \begin{mathpar}
     \openrule
         {
           \beta_{2j}^{j \in J_2'},\Pred_2,\Post_2 }
         {s_{20} \OTarrow {\alpha} s_{21}} 
\end{mathpar}
For each  weak open transition obtained above, we have  $(s_{11},t_x|\Pred_{s_{11},t_x})\in \mathcal{R}$  and $s_{11}=s_{20}$, so we have  $(s_{20},t_x|\Pred_{s_{20},t_x})\in \mathcal{R}$. Again 
 by Definition \ref{def-Weak-bisim} we can deduce there exist weak open transitions $\symb{WOT}_{x y}^{x\in X,y\in Y} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{j x y}^{j\in J_{x y}}, \Pred_{OT_{x y}},\Post_{OT_{x y}}}
         {t_x \OTWeakarrow {\alpha_{x y}} t_{x y}}
\end{mathpar}
 such that  $\forall x,\forall y, J_{xy}=\{j\in J_2'|\beta_{2j}\neq\tau\}, 
(s_{21},t_{x y}|\Pred_{s_{21},t_{x y}})\in \mathcal{R}$; \\
 $\Pred_{s_{11},t_x} \land \Pred_2\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{y\in Y}}
 \!\!  \left( \forall j\in J_{x y}. \vis{\beta_{2j}}\!=\!\gamma_{jx y}\Rightarrow \Pred_{OT_{x y}}\!\land \alpha\!=\!\alpha_{x y} \land  
     \Pred_{s_{21},t_{x y}}\subst{\Post_2\uplus\Post_{OT_{x y}}}\right)$

\item Similarly to the case 1,  the third  open transition in $\mathcal{T}_1$:
     \begin{mathpar}
%\inferrule{
 \openrule
    {
       \beta_{3j}^{j \in J_3'},\Pred_3,\Post_3   }
         {s_{30} \OTarrow {\tau} s_{31}} \in \mathcal{T}          
\end{mathpar}
From previous case, we have $(s_{21},t_{x y}|\Pred_{s_{21},t_{x y}})\in \mathcal{R}$, and we have $s_{21}=s_{30}$ then we have $(s_{30},t_{x y}|\Pred_{s_{30},t_{x y}})\in \mathcal{R}$. By
 Definition \ref{def-Weak-bisim} there exist weak open transition $\symb{WOT}_{x y z}^{x\in X,y\in Y,z\in Z} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{j x y z}^{j\in J_{x y z}}, \Pred_{OT_{x y z}},\Post_{OT_{x y z}}}
         {t_{x y} \OTWeakarrow {\alpha_{x y z}} t_{x y z}}
\end{mathpar}
 such that  $\forall x, \forall y, \forall z,J_{xyz}= \{j\in J_3'|\beta_{3j}\neq\tau\}, 
(s_{31},t_{x y z}|\Pred_{s_{31},t_{x y z}})\in \mathcal{R}$. \\
 $\Pred_{s_{21},t_{x y}} \land \Pred_3\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{z\in Z}}
   \!\left( \forall j\in J_{xyz}. \vis{\beta_{3j}}\!=\!\gamma_{j x y z} \! \Rightarrow\! \Pred_{OT_{x y z}}\!
     \land\! \alpha_{x y z}\!=\!\tau \land  
     \Pred_{s_{31},t_{x y z}}\subst{\Post_3\uplus\Post_{OT_{x y z}}}\right)$

@@

\begin{mathpar}
  \mprset {vskip=.5ex}
\inferrule {
\openrule
         {
           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTWeakarrow {\tau} t_x}
\qquad
\openrule
         {
           \gamma_{j x y}^{j\in J_{x y}}, \Pred_{OT_{x y}},\Post_{OT_{x y}}}
         {t_x \OTWeakarrow {\alpha_{x y}} t_{x y}}
\qquad
\openrule
         {
           \gamma_{j x y z}^{j\in J_{x y z}}, \Pred_{OT_{x y z}}, \Post_{OT_{x y z}}}
         {t_{x y} \OTWeakarrow {\tau} t_{x y z}}
\\
\set{\gamma}=\gamma_{j x}^{j\in J_{x}} \dotcup \gamma_{j x y}^{j\in J_{x y}} \subst{\Post_{OT_x}} \dotcup\gamma_{j x y z}^{j\in J_{x y z}} \subst{\Post_{OT_{x y}}\shortotimes\Post_{OT_x}}\\
\Pred=\Pred_{OT_x}\land\Pred_{OT_{x y}}\subst{\Post_{OT_x}}\land \Pred_{OT_{x y z}}\subst{\Post_{OT_{x y}}\shortotimes\Post_{OT_x}}\\
\Post= \Post_{OT_{x y z}} \shortotimes \Post_{OT_{x y}}\shortotimes\Post_{OT_{x}}\quad \alpha'_{x y}=\alpha_{x y}\subst{\Post_{OT_x}}\\
}
{
\openrule
         {
           \set{\gamma},
		\Pred, \Post}  
         {t \OTWeakarrow {\alpha'_{x y}} t_{x y z}} 
} 
 \end{mathpar}
So we need to prove that the following statement holds:\\
$\Pred_{s,t} \land \Pred\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}} \displaystyle{\bigvee_{y\in Y}}\displaystyle{\bigvee_{z\in Z}}
   \left( \forall j\in J_{x y z}. \gamma_j=\gamma_{j x y z}  \Rightarrow \Pred_{OT_{x y z}}
     \land \alpha \!=\! \alpha_{x y}' \land  
     \Pred_{s',t_{x y z}}\subst{\Post_{OT}\uplus\Post\,}\right)$

@@

The conjunction of the term $\Pred_2\subst{\Post_1}$ with the both sides of the implication, we get:\\  

@@

   \!\!\Big(\forall j\in J_x. \vis{\beta_{1j}}\!\!=\!\gamma_{jx}  \Rightarrow \Pred_{OT_x}
     \!\land\! \alpha_x\!=\!\tau \land\Big(\displaystyle{\bigvee_{y\in Y}}
    \forall j\in J_{x y}. \vis{\beta_{2j}}\!\!=\!\!\gamma_{jx y} \\ \Rightarrow \Pred_{OT_{x y}}\land \alpha\!=\!\alpha_{x y}\! \land \Pred_{s_{21},t_{x y}}\subst{\Post_2\uplus\Post_{OT_{x y}}}\Big)\subst{\Post_1\uplus\Post_{OT_x}} \Big)$\\
Furthermore, the rewriting of the formula  gives \TODO{ajouter argument $\alpha\!=\!\alpha_{x y} \subst{\Post_1\uplus\Post_{OT_x}}$ et $\vis{\beta_{2j}}\subst{\Post_1\uplus\Post_{OT_x}} \!=\!\gamma_{jx y}$}:\\

@@

\Big(\forall j\in J_x. \vis{\beta_{1j}}\!\!=\!\!\gamma_{jx} \land  \forall j \in J_{x y}. \vis{\beta_{2j}}\subst{\Post_1\uplus\Post_{OT_x}} \!=\!\gamma_{jx y}  \Rightarrow\Pred_{OT_x} \land  \Pred_{OT_{x y}} \subst{\Post_1\uplus\Post_{OT_x}} \land \alpha_x\!=\!\tau \land (\alpha\!=\!\alpha_{x y}) \subst{\Post_1\uplus\Post_{OT_x}} \land \Pred_{s_{21},t_{x y}}\subst{\Post_2\shortotimes\Post_1\uplus \Post_{OT_{x y}}\shortotimes \Post_{OT_x}}\Big)$\\ 
As $Post_1$  does not act on $\gamma_{jx y}$, nor on $ \Pred_{OT_{x y}}$ and $  \alpha_{x y}$, the formula can be simplified as follows:\\

@@

\Big(\forall j\in J_x. \vis{\beta_{1j}}\!=\!\gamma_{jx} \land  \forall j \in J_{x y}. \vis{\beta_{2j}}\subst{\Post_{OT_x}}\!=\!\gamma_{jx y}   \Rightarrow\Pred_{OT_x} \land  \Pred_{OT_{x y}} \subst{\Post_{OT_x}} \land \alpha_x\!=\!\tau \land \alpha\!=\!\alpha_{x y} \subst{\Post_{OT_x}} \land \Pred_{s_{21},t_{x y}}\subst{\Post_2\shortotimes\Post_1\uplus \Post_{OT_{x y}}\shortotimes \Post_{OT_x}}\Big)$\\ 

@@

\Big(\forall j\in J_x.\vis{\beta^1_j}\!=\!\gamma_{jx} \land  \forall j \in J_{x y}. \vis{\beta_{2j}}\subst{\Post_{OT_x}} \!=\!\gamma_{jx y} \Rightarrow \Pred_{OT_x}\land\Pred_{OT_{x y}}\subst{\Post_{OT_x}} \land \alpha_x\!=\!
\tau \land \alpha\!=\! \alpha_{x y} \subst{\Post_{OT_x}} \land (\Pred_{s_{21},t_{xy}} \land  \Pred_3) \subst{\Post_2\shortotimes \Post_1\uplus \Post_{OT_{x y}}\shortotimes\Post_{OT_x}} \Big)$\\ 
Again note that because of the domain independence of the substitution, we removed $\Post_1$ and  we  added  $\Post_{OT_{x y}}\shortotimes\,\Post_{OT_x}$ on the right side of the implication.\\
Finally, by replacing $(\Pred_{s_{21},t_{xy}} \land  \Pred_3)$

@@

\hspace{1cm} \implies\!\! \displaystyle{\bigvee_{x\in X}} \displaystyle{\bigvee_{y\in Y}} \displaystyle{\bigvee_{z\in Z}} 
\Big(\forall j\in J_x.\vis{\beta_{1j}}\!=\!\gamma_{jx} \land\!  \forall j \!\in\! J_{x y}.\vis{\beta_{2j}}\subst{\Post_{OT_x}}\!=\!\gamma_{jx y}   \land \\
 \forall j\!\in\! J_{x y z}. \vis{\beta_{3j}} \subst{\Post_{OT_{x y}}\shortotimes\Post_{OT_x}} \!=\!\gamma_{j x y z}  \Rightarrow  \Pred_{OT_x}\land\Pred_{OT_{x y}} \subst{\Post_{OT_x}} \land \\
  \Pred_{OT_{x y z}}\!\subst{\Post_{OT_{x y}}\shortotimes\,\Post_{OT_x}} \land \alpha_x\!=\!
\tau \!\land \alpha\!=\!\alpha_{x y} \subst{\Post_{OT_x}}\land \alpha_{x y z}\!=\!\tau \land \Pred_{s_{31},t_{x y z}}  \subst{\underbrace{\Post_3\shortotimes\Post_2\shortotimes\Post_1}_{\Post_{OT}}\uplus \underbrace{\Post_{OT_{x y z}}\shortotimes \Post_{OT_{x y}}\shortotimes\Post_{OT_x}}_{\Post}} \Big)$\\
Having $s_{31}=s'$ we can conclude:\\

>>>>

$
%\mprset {vskip=.5ex}
%\inferrule 
\Big(\forall i \in [1..n+1].\openrule
    {
       \set{\beta_{1i}},\Pred_{1i},\Post_{1i}   }
         {s_{1i} \OTarrow {\tau} s_{1(i+1)}} \in \mathcal{T} \,\wedge\,
\openrule
         {
           \set{\beta_2},\Pred_2,\Post_2 }
         {s_2 \OTarrow {\alpha} s'_2} \in \mathcal{T}
\, \wedge\\
~~\hspace{2.25cm}\forall i \in [0..m].\openrule
         {
           \set{\beta_{3i}},\Pred_{3i},\Post_{3i}   }
         {s_{3i} \OTarrow {\tau} s_{3(i+1)}}\! \in\! \mathcal{T}
\Big)  \implies\!  {
\openrule
         {
           \set{\gamma},
		\Pred, \Post
				 } {s'' \OTWeakarrow {\alpha'} s'} \in\WT
}
$
where\\
$
\alpha'=\alpha\displaystyle{\subst{\bigotimes_{j=n+1}^{1}\!\!\Post_j^1}}\\
s''=s_{10} \wedge s_{1(n+2)}=s_2 \wedge s'_2 = s_{30} \wedge s_{3(m+1)}=s'\\
\displaystyle{
\set{\gamma}=\mybigdotcup_{i=1}^{n+1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{1} \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=n+1}^{1}\Post_{1j}}} \dotcup \mybigdotcup_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}} }}
\\
\Pred=\bigwedge_{i=1}^{n+1}\Pred_{1i}\subst{\bigotimes_{j=i-1}^{1}\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j={n+1}}^{1}\Post_{1j}}\land\\ 
~\qquad\quad\Big(\bigwedge_{i=0}^m\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j={n+1}}^{1}\Post_{1j}}\Big)\\
\Post=\bigotimes_{j=m}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j={n+1}}^{1}\Post_{1j}
$

@@

\openrule
         {
           \beta_{2j}^{j\in J_2'},\Pred_2,\Post_2 }
         {s_{20} \OTarrow {\alpha'} s_{21}} \in \mathcal{T}_1
 \wedge
\forall i \in [0..m].\openrule
         {
           \beta_{3ij}^{j\in J_3'},\Pred_{3i},  \Post_{3i}  }
         {s_{3i} \OTarrow {\tau} s_{3(i+1)}} \in \mathcal{T}_1
\bigg)
\end{mathpar}
where\\
$
\displaystyle{\alpha=\alpha'\subst{\bigotimes_{j=n}^{0}\Post_{1j}}}\\
s=s_{10} \wedge s_{1(n+1)}=s_{20} \wedge s_{21} = s_{30} \wedge s_{3(m+1)}=s'\\
\displaystyle{
\gamma_j^{j\in J'}=\mybigdotcup_{i=0}^n \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=n}^{0}\Post_{1j}}} \dotcup \mybigdotcup_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}} }}
\\
\Pred_{OT}=\bigwedge_{i=0}^n\Pred_{1i}\subst{\bigotimes_{j=i-1}^{0}\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j=n}^{0}\Post_{1j}}\land\\ 
~\qquad\quad\Big(\bigwedge_{i=0}^m\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}}\Big)\\
\Post_{OT}=\bigotimes_{j=m}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}$

For the sake of simplicity, we prove the rule in the  restricted case where $n$ and $m$ to be equal to $1$, hence a single tau open transition will be considered on each side of the potentially visible one. The proof may be easily generalized to the multiple tau open transitions by using the same reasoning and (\WTTrois)~rule. Consider each open transition separately:
\begin{enumerate}
\item For the first open transition in $\mathcal{T}_1$:
\begin{mathpar}
%\inferrule{
 \openrule
    {
       \beta_{1j}^{j\in J_1'},\Pred_1,\Post_1   }
         {s_{10} \OTarrow {\tau} s_{11}}          
\end{mathpar}
we have $(s,t|\Pred_{s,t})\in\mathcal{R}$ by hypothesis and $s=s_{10}$. Thus, by  Definition \ref{def-Weak-bisim} we  can deduce there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {u \OTWeakarrow {\alpha_x} u_x}
\end{mathpar}
 such that  $\forall x,J_{x}=\{j\in J_1'|\beta_{1j}\neq\tau\}, u=t,  (s_{11},t_x|\Pred_{s_{11},u_x})\in \mathcal{R}$ and \\
 $\Pred_{s,t} \land \Pred_1\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}}
  \!\! \left( \forall j\in J_x.\vis{\beta_{1j}}=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
     \land \alpha_x\!=\!\tau \land  
     \Pred_{s_{11},u_x}\subst{\Post_1\uplus\Post_{OT_x}}\right)$

Note that, because $\AlgE\cap\AlgA=\emptyset$  (actions and expressions are disjoint) and $\alpha_x\!=\!\tau$ we have 
directly ($\alpha_x$ cannot be a variable, and cannot contain expressions/variables because $\tau$ has no parameter):
\begin{mathpar}
    \openrule
         {
           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {u \OTWeakarrow {\tau} u_x}
\end{mathpar}
\item Concerning the middle open transition in $\mathcal{T}_1$:
 \begin{mathpar}
     \openrule
         {
           \beta_{2j}^{j \in J_2'},\Pred_2,\Post_2 }
         {s_{20} \OTarrow {\alpha} s_{21}} 
\end{mathpar}
we have  $(s_{11},u_x|\Pred_{s_{11},u_x})\in \mathcal{R}$  and $s_{11}=s_{20}$. Again 
 by Definition \ref{def-Weak-bisim} we can deduce there exist weak open transitions $\symb{WOT}_{y}^{y\in Y} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{y}^{j\in J_{y}}, \Pred_{OT_{y}},\Post_{OT_{y}}}
         {u_x \OTWeakarrow {\alpha_{y}} v_{y}}
\end{mathpar}
 such that  $\forall y, J_{y}=\{j\in J_2'|\beta_{2j}\neq\tau\}, 
(s_{21},v_{y}|\Pred_{s_{21},v_{y}})\in \mathcal{R}$; \\
 $\Pred_{s_{11},u_x} \land \Pred_2\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{y\in Y}}
 \!\!  \left( \forall j\in J_{y}. \vis{\beta_{2j}}\!=\!\gamma_{jy}\Rightarrow \Pred_{OT_{y}}\!\land \alpha\!=\!\alpha_{y} \land  
     \Pred_{s_{21},v_{y}}\subst{\Post_2\uplus\Post_{OT_{y}}}\right)$

\item Similarly to the case 1,  the third  open transition in $\mathcal{T}_1$:
     \begin{mathpar}
%\inferrule{
 \openrule
    {
       \beta_{3j}^{j \in J_3'},\Pred_3,\Post_3   }
         {s_{30} \OTarrow {\tau} s_{31}} \in \mathcal{T}          
\end{mathpar}
From previous case, we have $(s_{21},v_{y}|\Pred_{s_{21},v_{y}})\in \mathcal{R}$, and we have $s_{21}=s_{30}$. Then, by
 Definition \ref{def-Weak-bisim} there exist weak open transition $\symb{WOT}_{x}^{z\in Z} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{jz}^{j\in J_{z}}, \Pred_{OT_{z}},\Post_{OT_{z}}}
         {v_{y} \OTWeakarrow {\tau} w_{z}}
\end{mathpar}
 such that  $\forall z, J_{z}= \{j\in J_3'|\beta_{3j}\neq\tau\}, 
(s_{31},w_{z}|\Pred_{s_{31},w_{z}})\in \mathcal{R}$,  $w_z=t_x$ and \\
 $\Pred_{s_{21},v_{y}} \land \Pred_3\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{z\in Z}}
   \!\left( \forall j\in J_{z}. \vis{\beta_{3j}}\!=\!\gamma_{jz} \! \Rightarrow\! \Pred_{OT_{z}}\!
     \land\! \alpha_{z}\!=\!\tau \land  
     \Pred_{s_{31},t_{x}}\subst{\Post_3\uplus\Post_{OT_{z}}}\right)$

@@

\begin{mathpar}
  \mprset {vskip=.5ex}
\inferrule {
\openrule
         {
           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTWeakarrow {\tau} u_x}
\qquad
\openrule
         {
           \gamma_{j y}^{j\in J_{y}}, \Pred_{OT_{ y}},\Post_{OT_{y}}}
         {u_x \OTWeakarrow {\alpha_{y}} v_{y}}
\qquad
\openrule
         {
           \gamma_{jz}^{j\in J_{z}}, \Pred_{OT_{z}}, \Post_{OT_{z}}}
         {v_{y} \OTWeakarrow {\tau} t_{x}}
\\ 
\set{\gamma'}=\gamma_{j x}^{j\in J_{x}} \dotcup \gamma_{j x y}^{j\in J_{x y}} \subst{\Post_{OT_x}} \dotcup\gamma_{j x y z}^{j\in J_{x y z}} \subst{\Post_{OT_{x y}}\shortotimes\Post_{OT_x}}\\
\Pred=\Pred_{OT_x}\land\Pred_{OT_{x y}}\subst{\Post_{OT_x}}\land \Pred_{OT_{x y z}}\subst{\Post_{OT_{x y}}\shortotimes\Post_{OT_x}}\\
\Post= \Post_{OT_{x y z}} \shortotimes \Post_{OT_{x y}}\shortotimes\Post_{OT_{x}}\quad \alpha'_{x y}=\alpha_{y}\subst{\Post_{OT_x}}\\
}
{
\openrule
         {
           \set{\gamma},
		\Pred, \Post}  
         {t \OTWeakarrow {\alpha'_{y}} t_{x}} 
} 
 \end{mathpar}
So we need to prove that the following statement holds:\\
$\Pred_{s,t} \land \Pred\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}} \displaystyle{\bigvee_{y\in Y}}\displaystyle{\bigvee_{z\in Z}}
   ( \forall j\in J. \gamma_j'=\gamma_{j}  \Rightarrow \Pred
     \land \alpha \!=\! \alpha_{y}' \land  
     \Pred_{s',t_{x}}\subst{\Post_{OT}\uplus\Post\,})$

@@

The conjunction of the predicate $\Pred_2\subst{\Post_1}$ with the both sides of the implication, we get:\\  

@@

   \!\!(\forall j\in J_x. \vis{\beta_{1j}}\!\!=\!\gamma_{jx}  \Rightarrow \Pred_{OT_x}
     \land \alpha_x\!=\!\tau \land\Big(\displaystyle{\bigvee_{y\in Y}}(
    \forall j\in J_{y}. \vis{\beta_{2j}}\!=\!\gamma_{jy} \\ \Rightarrow \Pred_{OT_{y}}\land \alpha'\!=\!\alpha_{y}\! \land \Pred_{s_{21},t_{y}'}\subst{\Post_2\uplus\Post_{OT_{y}}}\Big)\subst{\Post_1\uplus\Post_{OT_x}})$\\
Furthermore, the rewriting of the formula  gives:\\

@@

(\forall j\in J_x. \vis{\beta_{1j}}\!\!=\!\gamma_{jx} \land  \forall j \in J_{y}. (\vis{\beta_{2j}}\!=\!\gamma_{jy})\subst{\Post_1\uplus\Post_{OT_x}}   \Rightarrow\Pred_{OT_x} \land  \Pred_{OT_{x y}} \subst{\Post_1\uplus\Post_{OT_x}} \land \alpha_x\!=\!\tau \land (\alpha'\!=\!\alpha_{y}) \subst{\Post_1\uplus\Post_{OT_x}} \land \Pred_{s_{21},t_{y}'}\subst{\Post_2\shortotimes\Post_1\uplus \Post_{OT_{y}}\shortotimes \Post_{OT_x}})$\\ 
As $Post_1$  does not act on $\gamma_{jy}$, nor on $ \Pred_{OT_{y}}$ and $  \alpha_{y}$, as well $\Post_{OT_x}$  does not act on $\alpha'$, nor on  $\beta_{2j}$ the formula can be simplified as follows:\\

@@

(\forall j\in J_x. \vis{\beta_{1j}}\!=\!\gamma_{jx} \land  \forall j \in J_{y}. \vis{\beta_{2j}}\subst{\Post_1}=\gamma_{jy} \subst{\Post_{OT_x}}  \Rightarrow\Pred_{OT_x} \land  \Pred_{OT_{y}} \subst{\Post_{OT_x}} \land \alpha_x =\tau \land \alpha'\subst{\Post_1}=\alpha_{y} \subst{\Post_{OT_x}} \land \Pred_{s_{21},t_{y}'}\\\subst{\Post_2\shortotimes\Post_1\uplus \Post_{OT_{y}}\shortotimes \Post_{OT_x}})$\\ 

@@

\Big(\forall j\in J_x.\vis{\beta^1_j}\!=\!\gamma_{jx} \land  \forall j \in J_{y}. \vis{\beta_{2j}}\subst{\Post_1}\!=\!\gamma_{jy} \subst{\Post_{OT_x}}\Rightarrow \Pred_{OT_x}\land\Pred_{OT_{y}}\subst{\Post_{OT_x}} \land \alpha_x=\tau \land \alpha'\subst{\Post_1}= \alpha_{y} \subst{\Post_{OT_x}} \land \\(\Pred_{s_{21},t_{y}'} \land  \Pred_3) \subst{\Post_2\shortotimes \Post_1\uplus \Post_{OT_{y}}\shortotimes\Post_{OT_x}})$\\ 
Again note that because of the domain independence of the substitution, we removed $\Post_1$ and  we  added the term $\Post_{OT_{y}}\shortotimes\,\Post_{OT_x}$ in the substitution of the right side of the implication.\\
Finally, by replacing the predicate $(\Pred_{s_{21},t_{y}} \land  \Pred_3)$

@@

\Big(\forall\! j\in\! J_x.\vis{\beta_{1j}}\!=\!\gamma_{jx} \land  \forall j \!\in\! J_{y}.\vis{\beta_{2j}\subst{\Post_{OT_x}}}\!=\!\gamma_{jy} \subst{\Post_{OT_x}}  \land 
 \forall j\!\in\! J_{z}. \vis{\beta_{3j} \subst{\Post_2\,\shortotimes\,\Post_1}} \!=\!\gamma_{jz} \subst{\Post_{OT_{y}}\shortotimes\Post_{OT_x}}  \Rightarrow  \Pred_{OT_x}\land\Pred_{OT_{y}} \subst{\Post_{OT_x}} \land\\ 
  \Pred_{OT_{z}}\subst{\Post_{OT_{y}}\shortotimes\Post_{OT_x}} \land \alpha_x\!=\!
\tau \land \alpha'\subst{\Post_1}=\alpha_{y} \subst{\Post_{OT_x}}\land \alpha_{z}\!=\!\tau \land \Pred_{s_{31},t_{z}}  \subst{\underbrace{\Post_3\shortotimes\Post_2\shortotimes\Post_1}_{\Post_{OT}}\uplus \underbrace{\Post_{OT_{z}}\shortotimes \Post_{OT_{y}}\shortotimes\Post_{OT_x}}_{\Post}} \Big)$\\
Having $s_{31}=s'$ and $\alpha= \alpha'\subst{\Post_1}$ and rewriting the formula:\\ 
